---
title: 'Lesson Plan: 1.0'
author: "DCB"
date: "9/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Create an R chunk and 
load library for tidyverse

1) Using the green +c tab to create an r chunk , create empty chunk

2) add the below lines of code in chunk
 (note this has optional code to check to see if the tidyverse package is installed and to install it if necessary. This is advanced programing, not necessary)
 
3) execute chunk (green right arrow at top of chunk)

```{r}
if("tidyverse" %in% rownames(installed.packages()) == FALSE) {
  install.packages("tidyverse")
}
library(tidyverse)
```
### Use formating to show off
> Make complex sounding mission statement which actually says nothing, just like the big time politicians. 


Access the built in mpg datafile and view it
```{r}
data(mpg)
View(mpg)
```

Do a simple plot of engine displacement vs highway mpg
To make code easy, attach the dataframe 

```{r}
attach(mpg)
plot(displ, hwy)
```



